---
title: "Homework 3 Solution"
author: "Ling Yi"
date: "10/6/2020"
output: github_document
---



#Problem 1

Loading required packages

```{r setup, include=TRUE}
library(tidyverse)
library(p8105.datasets)
```


```{r}
data("instacart")
```

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))

##most items are from fresh vegetables

instacart %>% 
  distinct(aisle) %>% 
  count()

##there are 134 distinct aisles
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. Observations are the level of items in orders by user. There are user/order variables -- user ID, order ID, order day, and order hour. There are also item variables --name, aisle, department, and some numeric codes. 

##Let's make a plot

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n>10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x=aisle, y=n))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(
    title = "Items Ordered Plot",
    x = "Aisle",
    y = "Items ordered"
  )
```

##Making a table

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>%
  count(product_name) %>% ##This will keep aisle and counting the product name
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank<4) %>% 
  arrange(aisle,rank) %>% 
  knitr::kable()
```

apples vs ice cream..

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```





























