---
title: "Homework 3 Solution"
author: "Ling Yi"
date: "10/6/2020"
output: github_document
---



#Problem 1

Loading required packages

```{r setup, include=TRUE}
library(tidyverse)
```


```{r}

library(p8105.datasets)
data("instacart")
```

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))

##most items are from fresh vegetables

instacart %>% 
  distinct(aisle) %>% 
  count()

##there are 134 distinct aisles
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. Observations are the level of items in orders by user. There are user/order variables -- user ID, order ID, order day, and order hour. There are also item variables --name, aisle, department, and some numeric codes. 

##Let's make a plot

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n>10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x=aisle, y=n))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(
    title = "Items Ordered Plot",
    x = "Aisle",
    y = "Items ordered"
  )
```

##Making a table

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>%
  count(product_name) %>% ##This will keep aisle and counting the product name
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank<4) %>% 
  arrange(aisle,rank) %>% 
  knitr::kable()
```

apples vs ice cream..

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	) %>% 
  knitr::kable()
```

#Problem 2

#load and tidy data

```{r}
acceler_df = read_csv("./data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
      activity_1:activity_1440,
      names_to = "activity_num", 
      names_prefix = "activity_",
      values_to = "activity_counts"
  ) %>% 
  mutate(
      day_binary = ifelse(day ==  "Saturday" | day == "Sunday" , "weekend", "weekday"),
      activity_counts = as.numeric(activity_counts)
  )

``` 

##describing the data set

This data set contains information on five weeks of accelerometer data collected on a 63 year-old male with BMI of 25 diagnoised with congestive heart failure. The data set contains `r nrow(acceler_df)` rows and `r ncol(acceler_df)` variables. The variables included in this data set are `r names(acceler_df)`. Activity_counts describes the activity counts for each minute of a 24 hour day starting at midnight and day_binary categorizes days of the week into either 'weekend' or 'weekday'.


##table showing activity by day

```{r}
acceler_df %>% 
  group_by(week, day) %>% 
  summarize(sum_act = (sum(activity_counts)) 
 ) %>% 
  pivot_wider(
    names_from=day,
    values_from=sum_act
  ) %>% 
  knitr::kable()
```

##plot of minute and activity by day

```{r}
##work on this later
acceler_df %>% 
  mutate(
    activity_num = as.numeric(activity_num)
  ) %>% 
  ggplot(aes (x=activity_num, y=activity_counts, color = day))+
  geom_line(alpha = .5)+
  geom_smooth()+
    labs(
      title = "Plot of minute and activity counts", 
      x = "minute of the day", 
      y = "activity counts"
  )+
    scale_x_continuous(
    breaks = c(0,360, 720, 1080, 1440), 
    labels = c("0", "360", "720", "1080", "1440"))

```
The table shows activity counts by minute starting at midnight. We see that at minute 360 (6:00am) there is a spike in activity. Between 6:00am and noon, there are several (approximately 10 spikes) in activity and most of the activity is concentrated in the evening  (between minute 900 and 1200). We see more morning activity on Sunday and more evening activity on Friday. 

#Problem 3

```{r}
data("ny_noaa")
```

##clean and tidy data

```{r}
ny_noaa_df = ny_noaa %>%
    separate(date, into = c("year", "month", "day")) %>% 
    mutate(
      month = as.numeric(month), 
      prcp = as.numeric(prcp),
      tmin = as.numeric(tmin),
      tmax = as.numeric(tmax),
      year = as.factor(year)
  ) %>% 
   mutate(
    tmin = tmin/10,
    tmax = tmax/10,
    prcp = prcp/10
    )
    
month_df =
  tibble(
    month = 1:12,
    month_name=month.name
  ) 
ny_noaa_df = left_join(ny_noaa_df, month_df, by = "month") %>% 
   select(-c("month")) %>% 
   relocate("id", "year", "month_name", "day")
```

##common values for snowfall

```{r settings, message=FALSE}
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
ny_noaa %>% 
  mutate(
    snow = as.factor(snow)
  ) %>% 
  distinct(snow) %>% 
  count()
##Add in geom smooth
```

##Two panel plot

```{r}
ny_noaa_df %>% 
  group_by(id, year, month_name) %>% 
  filter(month_name == "January" | month_name == "July") %>% 
  summarize(avg_max = mean(tmax, na.rm=TRUE,)) %>% 
  ggplot(aes(x=year, y=avg_max, group = id))+
  geom_point()+
  geom_path(alpha = 05, size = .3)+
  facet_grid(~ month_name)+
  labs(
    title = "Average max temp. for January and July by station and year",
    x = "Year",
    y = "Average max temperature (C)"
  )+
  theme(legend.position = "none")

```


##making a hex plot

##making the plot for tmin and tmax
```{r}
library(hexbin)
library(patchwork)
  
tmax_tmin_plot = 
ny_noaa_df %>% 
   mutate(
    prcp = as.numeric(prcp),
    tmin = as.numeric(tmin),
    tmax = as.numeric(tmax)
  ) %>% 
  drop_na(tmax, tmin) %>% 
  ggplot(aes(x=tmax, y=tmin))+
  geom_hex()+
  labs(
    title = "Maximum and Minimum Tempterature (C)",
    x = "Minimun Temerature",
    y = "minimum Temperature"
      )
```

##making the snow fall plot

```{r, fig.height=6, fig.width =8}

snowfall_plot =  
  ny_noaa_df %>% 
  mutate(
    year = as.factor(year)
  ) %>% 
  filter(snow<=100 & snow>0) %>% 
  mutate(
    year = as.factor(year)
  ) %>% 
  ggplot(aes(x=year, y=snow, color = year))+
  geom_violin(aes(fill = year), alpha = .5)+
  theme(legend.position = "none")+
  labs(
    title = "Snowfall (mm) by year",
    x = "Year",
    y = "Snowfall (mm)"
      )
```

##combining the work with patchwork 

```{r}
tmax_tmin_plot/snowfall_plot
```



















