---
title: "Homework 3 Solution"
author: "Ling Yi"
date: "10/6/2020"
output: github_document
---



#Problem 1

Loading required packages

```{r setup, include=TRUE}
library(tidyverse)
library(p8105.datasets)
```


```{r}
data("instacart")
```

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))

##most items are from fresh vegetables

instacart %>% 
  distinct(aisle) %>% 
  count()

##there are 134 distinct aisles
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. Observations are the level of items in orders by user. There are user/order variables -- user ID, order ID, order day, and order hour. There are also item variables --name, aisle, department, and some numeric codes. 

##Let's make a plot

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n>10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x=aisle, y=n))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(
    title = "Items Ordered Plot",
    x = "Aisle",
    y = "Items ordered"
  )
```

##Making a table

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>%
  count(product_name) %>% ##This will keep aisle and counting the product name
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank<4) %>% 
  arrange(aisle,rank) %>% 
  knitr::kable()
```

apples vs ice cream..

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	) %>% 
  knitr::kable()
```

#Problem 2

#load and tidy data

```{r}
acceler_df = read_csv("./data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
      activity_1:activity_1440,
      names_to = "activity_num", 
      names_prefix = "activity_",
      values_to = "activity_counts"
  ) %>% 
  mutate(
      day_binary = ifelse(day ==  "Saturday" | day == "Sunday" , "weekend", "weekday"),
      activity_counts = as.numeric(activity_counts)
  )

``` 

##describing the data set

This data set contains information on five weeks of accelerometer data collected on a 63 year-old male with BMI of 25 diagnoised with congestive heart failure. The data set contains `r nrow(acceler_df)` rows and `r ncol(acceler_df)` variables. The variables included in this data set are `r names(acceler_df)`. Activity_counts describes the activity counts for each minute of a 24 hour day starting at midnight and day_binary categorizes days of the week into either 'weekend' or 'weekday'.


##table showing activity by day

```{r}
acceler_df %>% 
  group_by(week, day) %>% 
  summarize(sum_act = (sum(activity_counts)) 
 ) %>% 
  pivot_wider(
    names_from=day,
    values_from=sum_act
  ) %>% 
  knitr::kable()
```

##plot of minute and activity by day

```{r}
##work on this later
acceler_df %>% 
  ggplot(aes (x=activity_num, y=activity_counts, colors=day))+
  geom_point()
```


#Problem 3

```{r}
library(p8105.datasets)
data("ny_noaa")
```

##clean and tidy data

```{r}
ny_noaa = ny_noaa %>%
    separate(date, into = c("year", "month", "day"), convert = TRUE)

month_df=
  tibble(
    month = 1:12,
    month_name=month.name
  ) 
ny_noaa = left_join(ny_noaa, month_df, by = "month") %>% 
   select(-c("month")) %>% 
   relocate("id", "year", "month_name", "day")
```

##common values for snowfall

```{r}
ny_noaa %>% 
  mutate(
    snow = as.factor(snow)
  ) %>% 
  count()
```

##Two panel plot

```{r}
ny_noaa %>% 
  mutate(
    tmin = as.numeric(tmin),
    tmax = as.numeric(tmax)
  ) %>% 
  filter(month_name == "January" | month_name == "July") %>% 
  group_by(id, year, month_name) %>% 
  summarize(avg_max = mean(tmax, na.rm=TRUE,)) %>% 
  ggplot(aes(x=year, y=avg_max))+
  geom_point()+
  geom_path(aes(color = id), alpha = 05, show.legend=FALSE)+
  facet_grid(~ month_name)+
  labs(
    title = "Average max temp. for January and July by station and year",
    x = "Year",
    y = "Average max temperature (C)"
  )

```




















